---
title: "Gun Control Chi-Square"
author: "Camila Bobroff"
date: "11/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This: I'm Camila and I'm updating this markdown file here. 

```{r}
library(tidyverse)
gc_df <- read_csv("gc_df.csv")

```

We are asking: Is there a signficant difference in recommended gun control action for male and female respondents (should guns be easier, harder, or the same difficulty to get)?

Hi Camila :) I am going to test if you can see these changes.

Camila: data wrangling and counts

```{r}
get_guns <- gc_df %>% 
  filter(gender != "NA", make_get_guns != "NA") %>% 
  count(gender, make_get_guns) %>% # Count how many people chose each opinion based on gender
  spread(make_get_guns, n) %>% # Spread out the make_get_guns designations by n (counts)
  select(-gender)

rownames(get_guns) <- c("Female", "Male") # Change row names in df such that only numbers exist in the center
```

This is Corinna, the collaborator. I am going to do a chi-squared test for independence

We ask, "Is there a significant association between sex and opinion on whether guns should be more difficult, easier, or the same difficulty to get.""

```{r}

# Let's look at the actual proportions:

guns_prop <- prop.table(as.matrix(get_guns), 1) # Updates get_guns to a matrix for it to work in prop.table. The 1 is the margin over which to calculate proportion
guns_prop



# Run a chi-squared test for independence

#H0: No significant difference between proportions in male and female

guns_x2 <- chisq.test(get_guns)
guns_x2

```

"recommended government action on gun access differed significantly between male (n = ) and female (n = ) respondents ($\chi^2${`r guns_x2$parameter`} = ....., p < 0.001). Notably, a much higher proportion of female respondents (57.4%) recommended making it more difficult to get guns, compared to 40.4% for males.

